The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-22 EducProposal.Rmd
Re-edited chart formatting

<br>
<p align="center">
[<img align="center" src="img/OECDChart.png" alt="Factors Affecting Entrepreneurship" height=350 width=450 />](img/OECDChart.png)</br>
</p>
<p align="center">
Source: OECD Local Entrepreneurship Reviews [@OECD2009]
</p>
### References

>>>>

<p align="center">
[<img align="center" src="img/OECDChart.png" alt="Factors Affecting Entrepreneurship" height=350 width=450 />](img/OECDChart.png)</br>
</p>
<p align="center">
Source: OECD Local Entrepreneurship Reviews [@OECD2009]
</p>

### References
